Devphotodraw_main_anlayses

### 2021-06-19 analysis/step4b_download_recognition_data/preprocess_recognition_data.Rmd
update data compilation and main analysis files

# compile all output csvs
```{r}
for (batch in 1:4){
  this_batch = read.csv(paste0("csv_out/",'batch',  batch, '_production_june2021.csv')) 
  if (batch==1) {
    all_data = this_batch
  }
  else {
    all_data <- all_data %>%
      full_join(this_batch)
  }
}

@@

# filter out participants who don't finish
```{r}
included_subs <- d %>%
  group_by(subID) %>%
  summarize(num_drawings = length(unique(image_name_short))) %>%
  filter(num_drawings > 140)

@@

# Preprocess recognition data for merging with classificatinos, etc
```{r}
humans <- d %>%
  rename(category = drawn_category) %>%
  # get site and unique ids from filenanme
  mutate(unique_ids = str_split_fixed(imageName, '_',6)[,6]) %>%
  mutate(unique_ids = str_split_fixed(unique_ids, '.png',2)[,1]) %>%
  mutate(site = case_when( is.na(str_locate(unique_ids,'photodraw_e2')[,1]) ~ "THU", 
                           !is.na(str_locate(unique_ids,'photodraw_e2')[,1]) ~ "CDM")) %>%
  mutate(unique_ids = case_when(site == "CDM" ~ str_split_fixed(unique_ids, '_',2)[,2],
                                site == "THU" ~ unique_ids)) %>%
  mutate(guessed_category = as.character(guessed_category)) %>%
  # clean up two guesses that somehow overrode drop down menU?
  mutate(guessed_category = case_when(guessed_category == "carn" ~ "car",
                                guessed_category == "hatb" ~ "hat",
                                TRUE ~ guessed_category)) %>%
  # make factors
  mutate(guessed_category = as.factor(guessed_category)) %>%
  mutate(unique_ids = as.factor(unique_ids)) %>%
  # calculate whether a guess was correct or not
  mutate(correct_or_not = guessed_category == category) %>%
  select(-subID)

@@

```{r}
write.csv(humans, here::here('data/compiled/recognition_ratings/compiled_data_test.csv'))
```

>>>>

# compile all output csvs
```{r}
for (batch in 1:21){
  this_batch = read.csv(paste0("csv_out/",'batch',  batch, '_production_june2021.csv')) 
  if (batch==1) {
    all_data = this_batch
  }
  else {
    all_data <- all_data %>%
      full_join(this_batch)
  }
}

@@

# filter out participants who don't finish
```{r}
included_subs <- d %>%
  group_by(subID) %>%
  summarize(num_drawings = length(unique(image_name_short))) %>%
  filter(num_drawings > 50)

@@

# Preprocess recognition data for merging with classificatinos, etc
```{r}
humans <- d %>%
  rename(category = drawn_category) %>%
  # get site and unique ids from filenanme
  mutate(unique_ids = str_split_fixed(imageName, '_',6)[,6]) %>%
  mutate(unique_ids = str_split_fixed(unique_ids, '.png',2)[,1]) %>%
  mutate(site = case_when(is.na(str_locate(unique_ids,'photodraw_e2')[,1]) ~ "THU", 
                           !is.na(str_locate(unique_ids,'photodraw_e2')[,1]) ~ "CDM")) %>%
  mutate(unique_ids = case_when(site == "CDM" ~ str_split_fixed(unique_ids, '_',2)[,2],
                                site == "THU" ~ unique_ids)) %>%
  mutate(guessed_category = as.character(guessed_category)) %>%
  # clean up two guesses that somehow overrode drop down menU?
  mutate(guessed_category = case_when(guessed_category == "carn" ~ "car",
                                guessed_category == "hatb" ~ "hat",
                                TRUE ~ guessed_category)) %>%
  # make factors
  mutate(guessed_category = as.factor(guessed_category)) %>%
  mutate(unique_ids = as.factor(unique_ids)) %>%
  # calculate whether a guess was correct or not
  mutate(correct_or_not = guessed_category == category) %>%
  select(-subID)

@@

```{r}
write.csv(humans, here::here('data/compiled/recognition_ratings/compiled_human_recognition.csv'))
```

### 2021-06-19 analysis/step6_main_analyses/devphotodraw_main_analysis.Rmd
update data compilation and main analysis files

### Load human classification data
```{r}
humans <- read.csv(here::here('data/compiled/recognition_ratings/compiled_data_test.csv'))

humans_merged <- humans %>%
  group_by(unique_ids, category) %>% # group by each drawing of each category
  summarize(num_correct = mean(correct_or_not)) %>%
  left_join(d, by=c('unique_ids','category')) # join with classification data

@@

## Main descriptive anlayses 
### Compute accuracy by age, condition, site 
```{r descriptives-across-age}
cor_by_age_by_site_by_cond <- d %>%  
  group_by(session_id,category,condition,age_numeric, site) %>%
  summarize(avg_cor = mean(correct_or_not)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_cor") 
```

### Plot accuracy by age, condition, site 
```{r}
base_size_chosen=12; smooth_alpha=.2
ggplot(cor_by_age_by_site_by_cond, aes(age_numeric,mean, col = condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) + 
  theme_few(base_size = base_size_chosen) + 
  labs(x='Age', y='Classification accuracy') +
  ylim(0,1) + 
  geom_smooth(span=10, alpha=.2) + 
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
  facet_grid(~site)
```
### Compute effort/tracing by age, condition, site 
```{r}
draw_duration <- d %>%
  group_by(unique_ids,condition,age_numeric, site) %>%
  summarize(avg_draw_duration = mean(draw_duration)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_draw_duration")

@@

@@

@@

## Add in effort/tracing covariates — does effort mediate any of the differences we're seeing? Not really. Still see same main effects structure.
```{r}
full_model_with_effort <- glmer(correct_or_not ~ condition*scale(age_numeric)+site +
                      scale(avg_tracing_score) +
                      scale(mean_intensity) +
                      scale(draw_duration) +
                      scale(num_strokes) + 
                      (1 | unique_ids) +
                      (condition*scale(age_numeric)  | category),
      data = d, family="binomial", control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))

@@

>>>>

### Load human classification data
```{r}
humans <- read.csv(here::here('data/compiled/recognition_ratings/compiled_human_recognition.csv'))

humans_merged <- humans %>%
  group_by(unique_ids, category) %>% # group by each drawing of each category
  summarize(num_correct = mean(correct_or_not)) %>%
  left_join(d, by=c('unique_ids','category')) %>% # join with classification data 
  filter(!is.na(age))
```

@@

## Main descriptive anlayses 
### Compute accuracy by age, condition, site 
```{r descriptives-across-age}
cor_by_age_by_site_by_cond <- d %>%  
  group_by(unique_ids,category,condition,age_numeric, site) %>%
  summarize(avg_cor = mean(correct_or_not)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_cor") %>%
  mutate(who = "model")

cor_by_age_by_site_by_cond_humans <- humans_merged %>%  
  group_by(unique_ids,category,condition,age_numeric, site) %>%
  summarize(avg_cor = mean(num_correct)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_cor") %>%
  mutate(who = 'humans')

humans_and_models <- cor_by_age_by_site_by_cond %>%
  full_join(cor_by_age_by_site_by_cond_humans)
```

### Plot accuracy by age, condition, site 
```{r}
base_size_chosen=12; smooth_alpha=.2
ggplot(humans_and_models, aes(age_numeric,mean, col = condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
  theme_few(base_size = base_size_chosen) + 
  labs(x='Age', y='Classification accuracy') +
  ylim(0,1) + 
  geom_smooth(span=10, alpha=.2) +
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
  facet_grid(who~site)
```
### Compute effort/tracing by age, condition, site 
```{r}
draw_duration <- d %>%
  group_by(unique_ids,condition,age_numeric, site) %>%
  summarize(avg_draw_duration = mean(draw_duration)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_draw_duration")

@@

```{r}
full_model_humans <- lmer(num_correct ~ condition*scale(age_numeric)*site +
                        (1 | unique_ids) +
                        (condition | category),
      data = humans_merged)
summary(full_model_humans)
```

@@

```{r}
full_model_no_int_humans <- lmer(num_correct ~ condition*scale(age_numeric)+site +
                        (1 | unique_ids) +
                        (condition | category),
      data = humans_merged)

summary(full_model_no_int_humans)

@@

## Add in effort/tracing covariates — does effort mediate any of the differences we're seeing? Not really. Still see same main effects structure.
```{r}
full_model_with_effort <- glmer(correct_or_not ~ condition*scale(age_numeric)*site +
                      scale(avg_tracing_score) +
                      scale(mean_intensity) +
                      scale(draw_duration) +
                      scale(num_strokes) + 
                      (1 | unique_ids) +
                      (condition*scale(age_numeric)  | category),
      data = d, family="binomial", control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))

@@

## Repeat with human classificatinos
```{r}
full_model_with_effort <- lmer(num_correct ~ condition*scale(age_numeric)*site +
                      scale(avg_tracing_score) +
                      scale(mean_intensity) +
                      scale(draw_duration) +
                      scale(num_strokes) + 
                      (1 | unique_ids) +
                      (condition |category), data = humans_merged)

# condition*age slopes on categories won't converge
summary(full_model_with_effort)
```
